Current State of Knowledge Representation Systems for Robotics

### 2011-11-30 krs-survey.tex
Reorganized criteria lists following discussion with Michael
Also started to fill some criteria subsections.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compared features}
\label{sect|compared-features}

\subsection{Intrinsic features}
\label{sect|intrinsic-features}

\subsubsection{Expressiveness}
\label{sect|expressiveness}

\paragraph{Logic formalism}

@@

A large number of logic formalism do exist, we shall summarize below the most
relevant for system actually deployed in current robotic architectures.

@@

\paragraph{Open World and Close World Assumptions}

@@

\paragraph{(Non) Monotonic Reasoning}

@@

A monotonic system does not theoritically allow for knowledge retractation,
which is an important issue in the robotic context where the world model is
likely to be often altered.  However it is a practical issue only if the
reasoning process is \emph{continuous} during the whole robot's activity
lifespan. It is often possible to stop the reasoner, alter the knowledge, and
restart the inference process on a new domain.

\paragraph{Knowledge alteration possibilities}

\paragraph{Representation of uncertainty}

\paragraph{Representation of time}

\paragraph{Context and Microtheories}
Explicit modeling of context of knowledge / domain of validity

\subsubsection{Possible-Worlds and Agent-dependent models}
\label{sect|possible-worlds}

\subsubsection{Introspection}
\label{sect|introspection}
Support for introspection?

\subsection{Strategies to deal with the physical world}

@@

%%%%%
\subsection{Integration in robotic architectures}
\label{sect|integration-robot}

\paragraph{Relation to task planning}

@@

@@

\subsubsection{Interaction with humans}
\label{sect|hri}

Both as developers (KRS as a tool to make robot knowledge explicit to the
robot designer) and end-users (like natural language processing,...)

\subsubsection{Scalability and responsiveness}
\label{sect|scalability}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compared Features}
\label{sect|compared-features}

\subsection{What Can be Represented? The Expressiveness Question}
\label{sect|intrinsic-features}

%\subsubsection{Expressiveness}
%\label{sect|expressiveness}

\subsubsection{Introduction: main logic formalisms}

@@

A large number of logic formalism do exist, we shall summarize below the most
relevant for systems actually deployed in current robotic architectures.

@@

\subsubsection{Open World and Close World Assumptions}

@@

\subsubsection{Representation of uncertainty}

Sources of uncertainty for a robot are two-fold: uncertainty \emph{intrinsic}
to facts (like \emph{``It may rain tomorrow''}), uncertainty caused by
imperfect perception of the world (\emph{``Is the bottle really on the
table?''}). Most logics do not account explicitely for uncertainty. It must be
either relied on specific logics (like Bayesian logics) or on extensions of
classical logics.

\subsubsection{Representation of time}

As an agent acting at human-like time scale and dealing with temporal concepts
(like actions), a robot may want to represent, and possibly to reason, about
time. Time representation is split into two distinct abilities: representing
time points (both in the past -- which is roughly equivalent to assignment of
timestamps to events the robot perceives -- and in the future), and
representing \emph{passing time} (durations, timespans) like in \emph{``the
eggs will be cooked in 10 min''}.

We call a system that do not account for time (\ie that permanently lives in
present) \emph{atemporal}.

\subsubsection{Context modeling}

\emph{Knowledge is contextualized information}\fxfatal{Find someone respectable
how said that :-)}: it is essential for the robot to associate the facts it
represents to a \emph{context}. The context carries the keys for the
interpretation of the information. It covers the \emph{domain of validity} of
the facts, the \emph{common-sense} knowledge required to fill the gaps in the
representation\fxfatal{give an example}, \fxfatal{What more?}.

\subsubsection{Possible-Worlds and representing what others know}
\label{sect|possible-worlds}

Linked to the context representation, but seen from another angle, knowledge
representation systems may provide explicit ways to model other point of view
on the world. This ability is often refered as the \emph{perspective taking}
ability.

\subsubsection{Introspection: knowledge about the knowledge}
\label{sect|introspection}
Support for introspection?

\subsubsection{Modifying its knowledge}

%%%%%%%%%%
\subsection{Reasoning Techniques}

\subsubsection{Reasoning in uncertainty}

\subsubsection{(Non) Monotonic Reasoning}

@@

A monotonic system does not theoritically allow for knowledge retractation,
which is an important issue in the robotic context where the world model is
likely to be often altered.  However it is a practical issue only if the
reasoning process is \emph{continuous} during the whole robot's activity
lifespan. It is often possible to stop the reasoner, alter the knowledge, and
restart the inference process on a new domain.
\fxfatal{Rephrase to emphazise that when new evidences appear, it is anyway often a
good idea to restart the reasoner.}

\fxfatal{Mention that the 'change of world' issue can also be dealt with appropriate
time representation.}
\fxfatal{Mention that probabilistic reasoning lead to implicit non-monotonic reasoning}

@@

%%%%%%%%%%%%%%%%%
\subsection{Acquiring Knowledge}

%%%%%%%%%%%%%%%%%
\subsection{Practical Integration in Robotic Architectures}
\label{sect|integration-robot}

\subsubsection{The planning task}

@@

\paragraph{Language integration}

@@

\subsubsection{Monitoring and debugging}
\label{sect|debugging}

\subsubsection{Is it fast enough? Scalability and responsiveness}
\label{sect|scalability}
